Light inextensible strings under tension in the Schwarzschild geometry

### 2019-03-18 string_ajp.tex
move the Flamm diagram to the figures, also make it bigger
reword

\begin{figure}[h!] % Created by "flamm.R"
\centering
\includegraphics[width=70mm]{flamm_string.pdf}
\caption{Perspective view of Flamm's paraboloid with superimposed minimal-length
  path corresponding to a taut, light string}
\label{flamm}
\end{figure}

@@

Taking strings for which $r>1$ first,
figure~\ref{closest_approach_non_self_intersecting} shows a sequence
of non-self-intersecting numerical solutions to
equation~\ref{rdashdash}, rotated so that the tangential point of
closest approach occurs at~$\phi=0$.
Figure~\ref{closest_approach_self_intersecting} shows the
corresponding diagram for self-interesecting strings
(figure~\ref{light_closest_approach} shows comparable null geodesic
diagram for comparison).  A bisection technique reveals that if the
closest approach is greater than a critical value of~$\simeq
1.076109317(1)$, the string does not self-intersect; if the closest
approach is less than this value, then the string crosses itself
at~$\phi=\pi/2$.  As discussed above, if $\left(r'\right)^2=2r(r-1)$,
the string has a point of inflection at which point the radius of
curvature becomes infinite.  Figure~\ref{curvature_switch} shows
non-self intersecting strings rotated so that the point of inflection
occurs at~$\phi=0$; we see that the strings have a finite length in
which convex to the origin and two semi-infinite stretches in which
the curvature goes the other way.

@@

>>>>

@@

Taking strings for which $r>1$ first,
figure~\ref{closest_approach_non_self_intersecting} shows a sequence
of non-self-intersecting numerical solutions to
equation~\ref{rdashdash}, rotated so that the tangential point of
closest approach occurs at~$\phi=0$.
Figure~\ref{closest_approach_self_intersecting} shows the
corresponding diagram for self-interesecting strings
(figure~\ref{light_closest_approach} shows comparable null geodesic
diagram for comparison).  A bisection technique reveals that if the
closest approach is greater than a critical value of~$\simeq
1.076109317(1)$, the string does not self-intersect; if the closest
approach is less than this value, then the string crosses itself
at~$\phi=\pi/2$.  As discussed above, if $\left(r'\right)^2=2r(r-1)$,
the string has a point of inflection at which point the radius of
curvature becomes infinite.  Figure~\ref{curvature_switch} shows
non-self intersecting strings rotated so that the point of inflection
occurs at~$\phi=0$; we see that each string has a finite length in
which it is convex to the origin and two semi-infinite stretches in
which the curvature is negative.

@@

\begin{figure}[h!] % Created by "flamm.R"
\centering
\includegraphics[width=170mm]{flamm_string.pdf}
\caption{Perspective view of Flamm's paraboloid with superimposed minimal-length
  path corresponding to a taut, light string}
\label{flamm}
\end{figure}
